Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
update

Software debugging is difficult. In particular, the task of locating the faulty
code (\ie{}, fault localization) is particularly challenging. For that reason,
countless automated techniques have been proposed in the past to reduce the cost
of fault localization. \Rui{cite my TSE survey paper.}

@@

Model-based software diagnosis (MBSD) and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
some works of Wotawa}, a technique that traces back statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

This paper reports the results of a comprehensive study evaluating the
impact of combining \ds{} and \sfl{} to improve software fault
localization, a technique we coin as \comb{}. The intuition for the combination is that
several highly ranked statements, albeit covered by failing
executions, may be unrelated to the fault. Our empirical study involves
\numFaults{} faults from \numPrograms{} different programs comprised
in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
is frequently used to evaluate fault localization research. Prior work
reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation
or used archaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

The goal of this paper is to reassess whether the \comb{} approach
yields promising results under a more rigorous experimental
methodology and a larger dataset.\comments{The D4J dataset is about
  twice as large than the biggest test suite used in previous
  studies.} This study covers the following research questions:

\newcommand{\rqone}{How often does DS miss faulty statements?}
\newcommand{\rqthree}{How effective is the \comb{} approach?}

@@

>>>>

Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce the cost of fault localization.

@@

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. It is a black-box statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., basic blocks) based on coverage and the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.

@@

This paper reports the results of a comprehensive study evaluating the
impact of combining \ds{} and \sfl{} to improve software fault
localization. The intuition for the \comb{} combination is that
several highly ranked statements, albeit covered by failing
executions, may be unrelated to the fault. The study involves
\numFaults{} faults from \numPrograms{} different programs comprised
in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
is frequently used to evaluate fault localization research. Prior work
reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation
or used arcaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more rigorous experimental
methodology and a larger dataset.\comments{ The D4J dataset is about
  twice as large than the biggest test suite used in previous
  studies.} This study covers the following research questions:

\newcommand{\rqone}{How often does DS miss faulty statements?}
\newcommand{\rqthree}{How effective is the \comb{} combination?}

@@

This section provides details on our \sfl{}+\ds{} combination approach
and its heuristics.
